---
title: "ea_pilot_sim"
format: html
editor: visual
---

## Load Libraries

```{r}
library(tidyverse)

```

## Demographics & ID

```{r}

# Create a data frame with ID, Sex, and Age variables
df <- data.frame(ID = 1:7000,
                 sex = sample(c("Male", "Female"), 100, replace = TRUE),
                 age = round(rnorm(100, mean = 30, sd = 10)), 
                 country = sample(c("Brazil", "China", "Denmark", "Japan", "UK", "USA"), 100, replace = TRUE))

```

## Independent Variables

### Create "easim" function

This function will help simulate the questionnaire specific questions.

Here we have loop which selects i from the sequence defined by str_pad(1:qn, 2, "left", "0"). This sequence is simply 1:qn, but forced to be at least two digits, adding a "0" to the left if this is not the case. In the function **"qn"** defines the number of questions the questionnaire has.

The loop then combines each element of this index with the question label, defined by **qlab**. It then samples a response from the possible response vector **rlab**, with **rnum** defining the number of times this is sampled. This is then added to the data frame **df**.

**it would also be possible to specify the rate at which each element of the response vector has by adding a vector with these probabilities after "replace = TRUE".**

See anthropomorphism below for example.

```{r}
easim <- function(qn, qlab, rlab, rnum){

  for (i in str_pad(1:qn, 2, "left",  "0")){
    df[paste0(qlab, i)] <- sample(rlab, rnum, replace = TRUE)
  }

  return(df)

}
```

Here we define possible **rlabs**

```{r}

truth <- c("Absolutely Untrue", "Mostly Untrue", "Somewhat Untrue", "Can't Say True or False", "Somewhat True", "Mostly True", "Absolutely True")
           
agreement <- c("Strongly Disagree", "Moderately Disagree","Slightly Disagree","Neither Agree nor Disagree","Slightly Agree", "Moderately Agree","Strongly Agree")

truefalse <- c("True", "False")

```

### Cognitive Bias variables

EXAMPLE: For Anthropomorphism here we use the easim function we created above. Specifying 10 (the number of questions), anth\_ (the question label we want), agreement (the response vector we want to sample from), and 6000, the number of cases we want to simulate.

```{r}

#Anthropomorphism

df <- easim(10, "anth_", agreement, 7000)

#Promiscuous Teleology

#Schizotypy

df <- easim(16, "schz_", truefalse, 7000)

#Dualism

df <- easim(10, "dua_", agreement, 7000)

#mentalizing - has unique response

df <- easim(10, "mnt_", c("Definitely Agree", "Definitely Disagree", "Slightly Agree", "Slightly Disagree"), 7000)

```

### Motivational variables

```{r}

#Social Desirability

df <- easim(8, "sd_", truth, 7000)

#Existential Securirty (1)

#Existential Security (2)

df <- easim(3, "ss_", agreement, 7000)

df <- easim(3, "st_", agreement, 7000)

df <- easim(3, "wi_", agreement, 7000)


#Personal Need for Structure

df <- easim(10, "nfs_", agreement, 7000)

#Death Anxiety

df <- easim(12, "da_", agreement, 7000)

#Need for Meaning

df <- easim(10, "nfm_", agreement, 7000)





```

re reverse scored

```{r}

anth_revid <- c("01", "02", "06")



```

```{r}
df2 <- df %>%
  mutate_at(vars(starts_with("anth") & ends_with(anth_revid)), agree_rev) %>%
  mutate_at(vars(starts_with("anth") & !ends_with(anth_revid)), agree_norm)

```
